%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\renewcommand{\ULthickness}{0.2pt}
\contourlength{0.8pt}
\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\uline{#2}}}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

    \begin{center}
        \textbf{\Huge \scshape Brandon Li} \\ \vspace{1pt}
        \small 978-245-5532 $|$
        \href{mailto:jobs@brandonli.me}{jobs@brandonli.me} $|$
        \href{https://brandonli.me}{brandonli.me} $|$
        \href{https://linkedin.com/in/brandonli28}{linkedin.com/in/brandonli28} $|$
        \href{https://github.com/PulseBeat02}{github.com/PulseBeat02}
    \end{center}


%-----------EDUCATION-----------
    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {University of California, Los Angeles (UCLA)}{Expected June {{GRAD_YEAR}}}
    {Bachelor of Science in Computer Science}{Los Angeles, CA}
    \vspace{2mm}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
    \section{Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
    {Software Engineering Intern (Incoming)}{June 2026 -- Sept 2026}
    {Google (YouTube)}{San Bruno, CA}
    \vspace{1mm}
    \resumeSubheading
    {Software Engineering Intern}{June 2025 -- Sept 2025}
    {VideoLAN}{Remote}
    \resumeItemListStart
    \resumeItem{Developed C/C++ video filters (real-time visual effects and processing) for VLC Media Player (traffic cone).}
    \resumeItem{Integrated a SAM2 model module with OpenCV to enable real-time object segmentation for visual analysis.}
    \resumeItem{Implemented YuNet-based ML face detection for real-time tracking of 100+ faces in surveillance systems.}
    \resumeItem{Built fast video-to-GIF conversion with 5 dithering algorithms for customizable quality and performance.}
    \resumeItem{Analyzed the AV1 video-codec specification and studied dav1d decoding algorithms to deepen knowledge.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeSubheading
    {Software Developer Intern}{Feb. 2023 -- June 2023}
    {Halvex}{Remote}
    \resumeItemListStart
    \resumeItem{Designed MongoDB-based TypeScript RESTful APIs to fetch customer transactions and emails.}
    \resumeItem{Launched a JavaScript Discord bot to link 100+ customers' WHMCS accounts with Discord.}
    \resumeItem{Established secure OAuth2 gateway RESTful API using Express.js for account verification.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeSubheading
    {Java Mentor}{Sept. 2021 -- Feb. 2022}
    {Chelmsford Chinese Language School}{Remote}
    \resumeItemListStart
    \resumeItem{Taught 20 weekly 1-hour lessons to 10 middle/high-school students with varying coding experience.}
    \resumeItem{Raised nearly \$1,000 dollars for the non-profit, helping the school keep afloat during COVID-19.}
    \resumeItem{Spent 1-2 additional hours weekly preparing homework/slides to help students master material.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------
    \section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\href{https://github.com/PulseBeat02/yt-media-storage}{\textbf{yt-media-storage}} $|$ \emph{C++, Assembly/SIMD, FFmpeg, Coding Theory, Compression}}{Feb. 2026 -- Present}
    \resumeItemListStart
    \resumeItem{Popular C++ tool ({{YT_STORAGE_STARS}} stars, {{YT_STORAGE_FORKS}} forks) that encodes local files into YouTube videos for storage.}
    \resumeItem{Achieved a 100x speed-up using inline Assembly, SIMD intrinsics, and OpenMP parallelization.}
    \resumeItem{Designed lightweight Qt 6 UI and libsodium encryption, enhancing user experience and security.}
    \resumeItem{Uses robust CRC/Wirehair error-correction to novelly bypass YouTube's compression algorithm.}
    \resumeItem{Reached \#5 on Hacker News (Y Combinator) within 12 hours, generating thousands of views.}
    \resumeItem{Includes \href{https://www.youtube.com/watch?v=l03Os5uwWmk}{technical explanation video} with over {{YT_IMPRESSIONS}} impressions, educating over {{YT_VIEWERS}} viewers.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeProjectHeading
    {\href{https://github.com/PulseBeat02/mcav}{\textbf{mcav}} $|$ \emph{Java, Spring Boot, TypeScript, CI/CD}}{June 2020 -- Present}
    \resumeItemListStart
    \resumeItem{Popular Java framework ({{MCAV_STARS}} stars, {{MCAV_FORKS}} forks) for building fast and portable media applications.}
    \resumeItem{Integrates with VLC/mpv with a documented image-processing pipeline API for easier adoption.}
    \resumeItem{Uses Spring Boot to stream sub-100ms latency audio to usable TypeScript/Howler.js frontend.}
    \resumeItem{Configured CI/CD pipeline with TeamCity using Oracle Cloud to automate software releases.}
    \resumeItem{Engineered native media player via JavaCV that is 5x faster than most pure-Java players.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeProjectHeading
    {\href{https://github.com/PulseBeat02/video-player}{\textbf{Pulse Media Player}} $|$ \emph{C++, OpenGL, OpenAL, FFmpeg}}{Feb. 2026 -- Present}
    \resumeItemListStart
    \resumeItem{Robust C++ media player written in less than 1K lines of code with small UI.}
    \resumeItem{Built a GPU-accelerated OpenGL shader pipeline for smooth 1080p playback.}
    \resumeItem{Supports OpenAL for automated audio device selection and smooth playback.}
    \resumeItemListEnd
    \vspace{1mm}
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
    \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}{: Java, C/C++, JavaScript/TypeScript, Assembly, OCaml} \\
        \textbf{Frameworks \& Libraries}{: Spring, Hibernate, FFmpeg, OpenCV, VLC, React, Next.js, Tailwind} \\
        \textbf{Technologies}{: Git, MongoDB, Google Cloud, Oracle Cloud} \\
        \textbf{Awards}{: USACO Gold, Google Foobar}
    }}
    \end{itemize}


%-------------------------------------------
\end{document}
